---
title: "A3: Incarceration"
output: html_document
---

### Introduction

I will be investigating the differences in incarceration rates between genders in this project. By examining how much the percentage of men and women incarcerated varies across the nation, we can gain a clearer understanding of any gender-based discrimination in the legal system.



### Summary Information

My research revealed a significant disparity in the number of men and women incarcerated. As of the most recent date in 2018, there were 6.2014802^{5} (620148) men incarcerated overall, while there were 1.0383795^{5} (103837.9) women. 2008 had the highest number of male inmates, with 6.8061372^{5} (680613.7) in prison. With 1.0383795^{5} (103837.9) females incarcerated, 2018 is the year with the largest number of females. For men, the average change (increase) in the number of people going to jail is 9907.3333333, while for women, it is 2001.6866667.




### The Dataset

The Vera Institute of Justice, which provides county and jurisdiction-level jail and prison data from 1970 to 2018 and 1983 to 2016, is the source of the Incarceration Trends data. The data covers a wide range of incarceration patterns both nationally and over a long period of time, as well as ongoing updates in recent years, thanks to the substantial research and grants. Additionally, Vera kept updating the data set with funds and more study. The dataset was gathered since state-level data has historically been the focus of incarceration research. By identifying county-level variations in US incarceration rates and delving into a wider range of factors, the researchers hoped to obtain more robust data.

There are 153,811 observations in this data, and the conclusions rangeThis dataset has 153,811 observations that span 121 characteristics. One must use caution when drawing conclusions about the entire population based on a result since any conclusions drawn from analyzing or visualizing this data set would just be a correlation. The problem of incarceration is extremely delicate and takes into account several factors, including gender, color, geography, and demographics, which can differ significantly throughout numerous persons. The amount of unknown numbers in the data, which may have resulted from dubious data gathering decades ago or from remote locations with scant incarceration data, is one of the data set's limitations. This may change how accurate it is.


### Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The first chart that you will create and include will show the trend over time of your variable/topic. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - This may mean showing the same measure for different locations or different racial groups. Think carefully about a meaningful comparison of locations (e.g., the top 10 counties in a state, top 10 states, etc.)
- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear legend title

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, code = readLines("chart1_example.R")}
```
``````{r, echo = FALSE, message = FALSE, code = readLines("Chart1.R")}
```

### Variable Comparison Chart

``````{r, echo = FALSE, message=FALSE, warning=FALSE, code = readLines("chart2.R")}
```

Scatter plots showing the relationship of proportion of the **overall county population** that female/male and proportion of female/male population **in jail**.

The second chart that you will create and include will show how two different (continuous) variables are related to one another. Again, think carefully about what such a comparison means and what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- You must have clear x and y axis labels
- The chart needs a clear title 
- If you choose to add a color encoding (not required), you need a legend for your different color and a clear legend title

### Map

``````{r, echo = FALSE, message = FALSE, code = readLines("map.R")}
```

The last chart that you will create and include will show how a variable is distributed geographically. Again, think carefully about what such a comparison means and what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Your map needs a title
- Your color scale needs a legend with a clear label
- Use a map based coordinate system to set the aspect ratio of your map

